Designing Modular Software: A Case Study in Introductory Statistics

### 2017-01-04 jcgs-paper-2016/final_submission/paper.tex
Use rsconnect instead of shinyapps

If the intent is to use a specific instance of \texttt{intRo} where many
students will access it at the same time, such as in an introductory
statistics class, it may be preferable to deploy a custom instance of
\texttt{intRo} to a publicly accessible URL. The package provides a
function \texttt{deploy\_intRo} which is a wrapper for the
\texttt{deployApp} function contained in the shinyapps package. Once the
shinyapps package is installed and configured, \texttt{deploy\_intRo}
will upload \texttt{intRo} as an application on the instructor's
ShinyApps.io account. The function takes the same arguments as
\texttt{run\_intRo}, so it can be deployed with a custom selection of
modules, and a customized theme. It also takes an additional argument
\texttt{google\_analytics}, which allows the specification of a Google
Analytics tracking ID. It also takes \texttt{...} as additional
arguments to be passed into the \texttt{deployApp} routine. For example,
if we wished to deploy the instance of \texttt{intRo} we ran previously,
we would call it like so:

>>>>

If the intent is to use a specific instance of \texttt{intRo} where many
students will access it at the same time, such as in an introductory
statistics class, it may be preferable to deploy a custom instance of
\texttt{intRo} to a publicly accessible URL. The package provides a
function \texttt{deploy\_intRo} which is a wrapper for the
\texttt{deployApp} function contained in the rsconnect package. Once the
rsconnect package is installed and configured, \texttt{deploy\_intRo}
will upload \texttt{intRo} as an application on the instructor's
ShinyApps.io account. The function takes the same arguments as
\texttt{run\_intRo}, so it can be deployed with a custom selection of
modules, and a customized theme. It also takes an additional argument
\texttt{google\_analytics}, which allows the specification of a Google
Analytics tracking ID. It also takes \texttt{...} as additional
arguments to be passed into the \texttt{deployApp} routine. For example,
if we wished to deploy the instance of \texttt{intRo} we ran previously,
we would call it like so:

### 2017-01-04 jcgs-paper-2016/paper.Rmd
Use rsconnect instead of shinyapps

If the intent is to use a specific instance of `intRo` where many students will access it at the same time, such as in an introductory statistics class, it may be preferable to deploy a custom instance of `intRo` to a publicly accessible URL. The package provides a function `deploy_intRo` which is a wrapper for the `deployApp` function contained in the shinyapps package. Once the shinyapps package is installed and configured, `deploy_intRo` will upload `intRo` as an application on the instructor's ShinyApps.io account. The function takes the same arguments as `run_intRo`, so it can be deployed with a custom selection of modules, and a customized theme. It also takes an additional argument `google_analytics`, which allows the specification of a Google Analytics tracking ID. It also takes `...` as additional arguments to be passed into the `deployApp` routine. For example, if we wished to deploy the instance of `intRo` we ran previously, we would call it like so:

>>>>

If the intent is to use a specific instance of `intRo` where many students will access it at the same time, such as in an introductory statistics class, it may be preferable to deploy a custom instance of `intRo` to a publicly accessible URL. The package provides a function `deploy_intRo` which is a wrapper for the `deployApp` function contained in the rsconnect package. Once the rsconnect package is installed and configured, `deploy_intRo` will upload `intRo` as an application on the instructor's ShinyApps.io account. The function takes the same arguments as `run_intRo`, so it can be deployed with a custom selection of modules, and a customized theme. It also takes an additional argument `google_analytics`, which allows the specification of a Google Analytics tracking ID. It also takes `...` as additional arguments to be passed into the `deployApp` routine. For example, if we wished to deploy the instance of `intRo` we ran previously, we would call it like so:
